---
title: ""
output: 
    pdf_document:
        latex_engine: lualatex
mainfont: georgia

header-includes:
 \usepackage{xcolor,colortbl}
 \usepackage{tabularx}
 \newcommand{\bcenter}{\begin{center}}
 \newcommand{\ecenter}{\end{center}}
 \usepackage[most]{tcolorbox}
 \usepackage{array, tabularx, caption, boldline}
 \usepackage{cellspace}
 \graphicspath{{Figures/}}
 \usepackage{grffile}
 \usepackage{graphicx}
 \usepackage{enumitem}
 \usepackage{longtable}
  \usepackage{xltabular}
  \usepackage{fancyhdr}
  \usepackage{ragged2e}
 \usepackage{geometry}
  \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 right=20mm,
 top=20mm,
 }
 

always_allow_html: true
params:
  starttime: "starttime"
  startdate: "startdate"
  participants: "participants"
  what: "what"
  potentialppl: "potentialppl"
  potentialenv: "potentialenv"
  potentialass: "potentialass"
  potentialrep: "potentialrep"
  planppl: "planppl"
  planenv: "planenv"
  planass: "planass"
  planrep: "planrep"
  notppl: "notppl"
  notenv: "notenv"
  notass: "notass"
  notrep: "notrep"
  shortcons: "shortcons"

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, include=FALSE}
library(stringr)
participants = str_replace_all(params$participants,"\n",", ")
potentialppl = str_replace_all(params$potentialppl,"\n"," \\\\linebreak ")
potentialenv = str_replace_all(params$potentialenv,"\n"," \\\\linebreak ")
potentialass = str_replace_all(params$potentialass,"\n"," \\\\linebreak ")
potentialrep = str_replace_all(params$potentialrep,"\n"," \\\\linebreak ")
planppl = str_replace_all(params$planppl,"\n"," \\\\linebreak ")
planenv = str_replace_all(params$planenv,"\n"," \\\\linebreak ")
planass = str_replace_all(params$planass,"\n"," \\\\linebreak ")
planrep = str_replace_all(params$planrep,"\n"," \\\\linebreak ")
notppl = str_replace_all(params$notppl,"\n"," \\\\linebreak ")
notenv = str_replace_all(params$notenv,"\n"," \\\\linebreak ")
notass = str_replace_all(params$notass,"\n"," \\\\linebreak ")
notrep = str_replace_all(params$notrep,"\n"," \\\\linebreak ")
```



\definecolor{myblue}{RGB}{0,60,113}
\definecolor{myred}{RGB}{218, 41, 28}
\setlist[itemize]{leftmargin=*}


   

\addtolength{\oddsidemargin}{-.3in}
\addtolength{\evensidemargin}{-.3in}
\addtolength{\textwidth}{-2in}
\pagestyle{fancy}
\fancyhf{}
\cfoot{\colorbox{myred}{\parbox{18cm}{\textbf{\color{white}{\Large \hspace{1.5cm}  Norwegian Hull Club Emergency Phone: +47 22 42 88 44  }}}} }
\renewcommand{\headrulewidth}{0pt}
 
 \colorbox{myblue}{\parbox{18cm}{\textbf{\color{white}{\huge \hspace{5cm} First meeting report \hspace{3cm}   \\}}}}

 \begin{flushleft}
 
 \textbf {Meeting date:} `r params$startdate`\hspace{2cm}
 \textbf {Start time:} `r params$starttime` \hspace{1.5cm}
 \textbf \hfill {End time:} `r Sys.time()`
 
 \textbf {Participants:} `r participants`



 \renewcommand{\arraystretch}{1.4}
 \begin{xltabular}{18cm} {|p{4.5cm}|>{\raggedright\arraybackslash}X |>{\raggedright\arraybackslash}X |>{\raggedright\arraybackslash}X|>{\raggedright\arraybackslash}X|}
 \hline
 \endfirsthead
 \rowcolor{myblue} \textcolor{white} {\textbf {Time: `r params$starttime`}} & \multicolumn{4}{|c|}{\textcolor{white}{\textbf {\Large First meeting boarder}}} \\
 \hline
  \endhead
 \rowcolor{myblue} \textcolor{white} {\textbf {Time: `r params$starttime`}} & \multicolumn{4}{|c|}{\textcolor{white}{\textbf {\Large First meeting boarder}}} \\
 \hline
 \cellcolor{myblue} \textcolor{white}{\textbf {What has happened?}} 
 \textcolor{white}{\textit{\begin{itemize}[itemsep=0mm]
  \item Facts
  \item Overview 
  \item Use of Situation Plot
  \item People involved 
  \item Incident overview 
  \item What is done? \end{itemize}}} & \multicolumn{4}{|l|}{\raggedleft `r params$what`}\\
 \hline
 \cellcolor{myblue} \textcolor{white}{\textbf {Indicent potential / \newline Worst case?}}
 \textcolor{white}{\textit{\begin{itemize}[itemsep=0mm] \item The potential in the current situation \end{itemize}}} & \textbf {Peolpe:}
 
  `r potentialppl` & \textbf {Environment:}

  `r potentialenv`& \textbf {Assets:}
  
  `r potentialass`& \textbf {Reputation:}
  
  `r potentialenv`\\
 \hline
 \cellcolor{myblue} \textcolor{white}{\textbf {Rough plan / Need for resources}}
  \textcolor{white}{\textit{\begin{itemize}[itemsep=0mm]
  \item Need of external resources based on worst case
  \end{itemize}}}& 
  `r planppl`& 
  `r planenv`& 
  `r planass`& 
  `r planenv`\\
 \hline
 \cellcolor{myblue} \textcolor{white}{\textbf {Notification}} 
  \textcolor{white}{\textit{\begin{itemize}[itemsep=0mm]
  \item According to procedure? 
  \item Beyond procedure?
  \end{itemize}}}&
  `r notppl`& 
  `r notenv`& 
  `r notass`& 
  `r notenv`\\
 \hline
 \cellcolor{myblue} \textcolor{white}{\textbf {Any other business?}} 
  \textcolor{white}{\textit{\begin{itemize}[itemsep=0mm]\item Shift
  \item Daily routines 
  \item Immediate changes
  \item Customer support
  \item Night-/Daytime
  \item Weather 
  \item Time zones
  \item Time of year 
  \item Internal conditions 
  \item Other
  \end{itemize}
  }}& \multicolumn{4}{|l|}{`r params$shortcons`} \\
 \hline
 \end{xltabular}
 \end{flushleft}



